Supporting Information for "Geometric models overestimate lake depth due to imperfect slope measurement"

### 2020-11-26 figures/01_geometry.Rmd
adjust figure s9 dimensions

```{r slope_by_area_depth, echo=FALSE, message=FALSE, eval=TRUE, warning=FALSE, results='hide', fig.width=5.5, fig.height=4.2}

@@

gg_area <- ggplot(data = dt) +
   geom_point(aes(x = nearshore_slope_mean, y = inlake_slope_pnt, color = x_bins)) +
   geom_smooth(aes(nearshore_slope_mean, inlake_slope_pnt, color = x_bins),
               method = "lm", se = FALSE) + 
  facet_wrap(~shape_class) +
    ggtitle("Area (ha)")

@@

gg_depth <- ggplot(data = dt) +
   geom_point(aes(x = nearshore_slope_mean, y = inlake_slope_pnt, color = x_bins)) +
   geom_smooth(aes(nearshore_slope_mean, inlake_slope_pnt, color = x_bins),
               method = "lm", se = FALSE) +
    facet_wrap(~shape_class) +
    ggtitle("Max Depth (m)")

>>>>

```{r slope_by_area_depth, echo=FALSE, message=FALSE, eval=TRUE, warning=FALSE, results='hide', fig.width=5.7, fig.height=3.3}

@@

gg_area <- ggplot(data = dt) +
   geom_point(aes(x = nearshore_slope_mean, y = inlake_slope_pnt, color = x_bins)) +
   geom_smooth(aes(nearshore_slope_mean, inlake_slope_pnt, color = x_bins),
               method = "lm", se = FALSE) + 
  xlim(c(0, 0.6)) + ylim(c(0, 0.6)) +
  facet_wrap(~shape_class) +
    ggtitle("Area (ha)")

@@

gg_depth <- ggplot(data = dt) +
   geom_point(aes(x = nearshore_slope_mean, y = inlake_slope_pnt, color = x_bins)) +
   geom_smooth(aes(nearshore_slope_mean, inlake_slope_pnt, color = x_bins),
               method = "lm", se = FALSE) +
    xlim(c(0, 0.6)) + ylim(c(0, 0.6)) +
    facet_wrap(~shape_class) +
    ggtitle("Max Depth (m)")

### 2020-11-26 manuscript/si_template_2019.tex
adjust figure s9 dimensions

\begin{figure}
      \begin{center}
        \includegraphics[width=0.75\textwidth,keepaspectratio]{../figures/slope_by_area_depth-1}
      \end{center}
      \caption{Compare the mean lake slopes in concave and convex lakes of the same size and max depth.}\label{figS1}
    \end{figure}
\clearpage

>>>>

\begin{figure}
      \begin{center}
        \includegraphics[width=0.79\textwidth,keepaspectratio]{../figures/slope_by_area_depth-1}
      \end{center}
      \caption{Comparison between in-lake and nearshore slopes in concave and convex lakes of the same size and max depth.}\label{figS9}
    \end{figure}
\clearpage
